---
title: "Mini HW 4-1: Getting started with functions"
author: "Your Name"
date: "Today's date"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Due Thursday, November 2 through Github**

Your next assignment is to practice creating functions in `R`.

### Recap from Content 4-1

There are three key steps to creating a new function using the following format:
```{r eval=FALSE}
function_name <- function(argument_1, argument_2, ...) {
# function's body
# code to do the function's task using the variables argument_1 and argument_2 from above
  
}
```

(1) You need to pick a **name** for the function. You should make the name meaningful to the task the function does.

(2) You list the inputs of the function, called **arguments**, inside `function()`. For a single argument, we use `function(x)`.  For multiple arguments, we would have something like `function(x, y, z)`.  It can be helpful to give your arguments meaningful names as well!

(3) You place the code that does the task in the **body** of the function, a block between `{` and `}` that immediately follows `function(...)`.

### Assignment

1. The following code can be used to calculate a 95% confidence interval for a population mean based on sample of observations, as we learned in Public Health Biostatistics. Run this code and examine each of the created objects (`x`, `xbar`, `se`, `n`) to be sure you understand what the code is doing.
```{r}
x <- rnorm(100)

xbar <- mean(x)
n <- length(x)
se <- sd(x) / sqrt(n)

xbar + c(-2, 2) * se
```

Now convert this code to a function, called `mean_ci()`, that takes a vector and returns a 95% confidence interval around the mean of that vector.
```{r}
# place your code to define your function here

```

Once your function is complete, test your function on the following two vectors.  **If the function doesn't work as expected, see if you can update your code above to fix the problem!**

* A random sample from a uniform distribution: 
```{r eval=FALSE}
x <- runif(100)
mean_ci(x)
```

* A vector with some missing values:
```{r eval=FALSE}
x <- c(rnorm(30), NA, NA)
mean_ci(x)
```

2. Complete the following code to calculate a 95% confidence interval for the difference in two population means, as we learned in Public Health Biostatistics.  Feel free to add/store some intermediate calculations in your code to make it more easily understandable.

As a hint, remember that in Public Health Biostatistics we calculate confidence intervals as 
$$
estimate \pm 2*SE(estimate)
$$
And that for a difference in population means, our estimate is $\bar{X}_1-\bar{X}_2$.  And the standard error of this estimate is: 
$$SE(\bar{X}_1-\bar{X}_2) = \sqrt{s_1^2/n_1 + s_2^2/n_2}$$

```{r eval=FALSE}
x <- rnorm(100, mean=10, sd=5)
y <- rnorm(100, mean=15, sd=5)

# estimate of difference
estimate <- 

# standard error of the estimate
se <- 

estimate + c(-2, 2) * se
```

Now convert this code to a function, called `two_mean_ci()`, that takes two vectors and returns a 95% confidence interval around the difference in means for those vectors.  You might keep in mind any modification you had to make to account for missing values in #1 above.
```{r}
# place your code here

```

3. Complete the following code to calculate a 95% confidence interval for a difference in population proportions, as we learned in Public Health Biostatistics.  Feel free to add/store some intermediate calculations in your code to make it more easily understandable.

As a hint, remember that for a difference in population proportions, our estimate is $\hat{p}_1-\hat{p}_2$.  And the standard error of this estimate is: 
$$SE(\hat{p}_1-\hat{p}_2) = \sqrt{\frac{\hat{p}_1(1-\hat{p}_1)}{n_1} + \frac{\hat{p}_2(1-\hat{p}_2)}{n_2}}$$

```{r eval=FALSE}
x <- c(1, 0, 0, 0, 1, 1, 1, 0, 0, 0, 1)
y <- c(0, 1, 0, 0, 1, 0, 0, 1, 0, 1)

# sample proportions
n.x <- length(x)
p.x <- sum(x)/length(x)

n.y <- 
p.y <- 

# estimate of difference
estimate <- 

# standard error of the estimate
se <- 

estimate + c(-2, 2) * se
```

Now convert this code to a function, called `two_prop_ci()`, that takes two 0/1 vectors and returns a 95% confidence interval around the difference in proportions  of those vectors.  You might keep in mind any modification you had to make to account for missing values in #1 above.
```{r}
# place your code here

```

4. Complete our sequence of functions by creating a `prop_ci()` function that takes a vector of 0/1 values and returns a 95% confidence interval for a proportion, as we learned in Public Health Biostatistics.

As a hint, remember that for a single population proportion, our estimate is $\hat{p}$.  And the standard error of this estimate is: 
$$SE(\hat{p}) = \sqrt{\frac{\hat{p}(1-\hat{p})}{n}}$$

```{r}
# place your code here

```

___

When you are finished with your assignment, knit your file and submit through Github. To do so, follow the steps below.  (If your document didn't successfully knit, please reach out to me over email at `phbiostats@jhu.edu` so I can help you trouble-shoot the issue.)

* First you need to **commit** the changes you've made to the document.  Click the colorful Git button at the top of the RStudio window and select "Commit" from the menu.
* In the window that opens, **stage** your changes by clicking the check boxes next to the `Mini4-1.Rmd` file.
* In the "Commit message" box, type a short description of what changes you've made, something like: `Completed assignment`
* Click the "Commit" button on the bottom right.
* You'll see a window that will tell you about the changes that you've made.  Click "Close" to close the window.  You've successfully committed! You can close this commit window now.
* After committing, you must **push** your changes to the repository on Github.  Do this by clicking the colorful Git button again and select "Push Branch".  
* Again, you'll see a window open that tells you your changes have been pushed!
* If you want, you can look at your repository on [Github.com](https://github.com/) and should be able to see your changes there!  
* You've successfully submitted your assignment :)


